Supplementary Materials

### 2023-07-31 analysis/supplementary-materials/supp-mat.qmd
remove unused files and add code-folding to supp mat

---
title: "Supplementary Materials"
execute: 
  echo: false
  warning: false
knitr: 
  opts_chunk: 
    message: false
format: 
  html:
    toc: true
    code-fold: true
    embed-resources: true
  pdf:
    toc: true
bibliography: "../paper/references.bib"
---

>>>>

---
title: "Supplementary Materials"
execute: 
  echo: false
  warning: false
knitr: 
  opts_chunk: 
    message: false
format: 
  html:
    format-links: false
    echo: true
    toc: true
    code-fold: true
    embed-resources: true
  pdf:
    toc: true
bibliography: "../paper/references.bib"
---
